\documentclass[12pt]{article}
\usepackage[a4paper, top=0.8in, bottom=0.7in, left=0.8in, right=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{tcolorbox}
\usepackage[defaultfam,tabular,lining]{montserrat}

\setlength{\parindent}{0pt}
\pagestyle{fancy}
\setlength{\headheight}{27.11148pt}
\addtolength{\topmargin}{-15.11148pt}
\fancyhf{}
\fancyhead[L]{\textbf{Grading Guide: Opinion Writing}}
\fancyfoot[C]{\footnotesize \copyright Study Smart Tutors}
\sloppy

\begin{document}

\section*{Pass/Fail Grading Guide for Writing Prompt}

\subsection*{Scoring Criteria}

\begin{tcolorbox}[colframe=black!40, colback=gray!5, title=Pass Criteria]
To pass this writing prompt, the response must meet \textbf{all} the following criteria:
\begin{enumerate}
    \item \textbf{Purpose and Focus:} The response addresses the prompt with a clear opinion and remains focused throughout.
    \item \textbf{Organization:} The response includes an introduction, at least two supporting reasons with evidence, and a conclusion.
    \item \textbf{Evidence:} The response references information from \textbf{both sources} and uses specific details to support the opinion.
    \item \textbf{Conventions:} The response demonstrates a basic command of grammar, punctuation, and spelling with minimal errors that do not interfere with meaning.
\end{enumerate}
\end{tcolorbox}

\begin{tcolorbox}[colframe=black!40, colback=red!5, title=Fail Criteria]
A response fails if it meets \textbf{any} of the following conditions:
\begin{enumerate}
    \item \textbf{Off-Topic:} The response does not address the writing prompt.
    \item \textbf{Lack of Opinion:} The response does not include a clear opinion.
    \item \textbf{Insufficient Evidence:} The response does not reference information from both sources or includes irrelevant evidence.
    \item \textbf{Poor Organization:} The response lacks an introduction, supporting reasons, or conclusion.
    \item \textbf{Conventions Issues:} The response contains significant grammar, punctuation, or spelling errors that interfere with understanding.
\end{enumerate}
\end{tcolorbox}

\subsection*{Pass/Fail Determination}

\begin{tcolorbox}[colframe=black!40, colback=white, title=How to Determine Pass or Fail]
\textbf{Pass:} A response meets all the criteria in the Pass section and does not exhibit any of the issues in the Fail section. The student demonstrates an understanding of the prompt and provides sufficient evidence to support their opinion. \\
\textbf{Fail:} A response fails if it meets one or more of the criteria listed in the Fail section. The student does not sufficiently address the requirements of the writing prompt.
\end{tcolorbox}

\subsection*{Examples of Passing and Failing Responses}

\begin{tcolorbox}[colframe=black!40, colback=green!5, title=Example of a Passing Response]
The school should build a new science lab because it helps students learn through hands-on experiments and improves teamwork skills. For example, Source 1 states that "hands-on experiments make science easier to understand." This shows that students will better understand science concepts by doing experiments instead of only reading about them. Additionally, the text mentions that "a science lab supports group work and collaboration," which are important skills for future careers. Building a science lab is the best choice to prepare students for success.
\end{tcolorbox}

\begin{tcolorbox}[colframe=black!40, colback=red!5, title=Example of a Failing Response]
I think the school should build a science lab. Science is fun, and I like experiments. The school needs a lab. 
\end{tcolorbox}

\end{document}
