\documentclass[12pt]{article}
\usepackage[a4paper, top=0.8in, bottom=0.7in, left=0.8in, right=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{tcolorbox}
\usepackage[defaultfam,tabular,lining]{montserrat}

\setlength{\parindent}{0pt}
\pagestyle{fancy}

\fancyhf{}
\fancyhead[L]{\textbf{Answer Key: Modal Auxiliaries (can, may, must)}}
\fancyfoot[C]{\footnotesize © Study Smart Tutors}

\begin{document}

\section*{Answer Key: Modal Auxiliaries (can, may, must)}

\subsection*{Guided Practice Answers}
\begin{enumerate}[itemsep=1em]
    \item You \textbf{must} eat all your vegetables to grow strong.
    \item I \textbf{must} finish my project before Friday.
    \item We \textbf{can} go outside to play if it stops raining.
    \item The teacher said we \textbf{may} use calculators for the test.
    \item Drivers \textbf{must} obey traffic signs to keep everyone safe.
\end{enumerate}

\subsection*{Independent Practice Answers}
\begin{enumerate}[itemsep=1em]
    \item You \textbf{must} bring your water bottle to stay hydrated.
    \item Visitors \textbf{must} sign in at the front desk.
    \item I \textbf{can} stay up late to finish my homework.
    \item We \textbf{may} go to the park if the weather is nice.
    \item Students \textbf{must} respect their classmates.
\end{enumerate}

\subsection*{Exit Ticket Sample Answers}
\textbf{Sample Sentences:}
\begin{itemize}
    \item \textbf{Can:} I can swim across the pool in one minute. (*ability*)
    \item \textbf{May:} You may borrow my book if you promise to return it. (*permission*)
    \item \textbf{Must:} We must arrive at school on time every day. (*necessity*)
\end{itemize}

\end{document}
