\documentclass[12pt]{article}
\usepackage[a4paper, top=0.8in, bottom=0.7in, left=0.8in, right=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{tcolorbox}
\usepackage[defaultfam,tabular,lining]{montserrat}

\setlength{\parindent}{0pt}
\pagestyle{fancy}

\fancyhf{}
\fancyhead[L]{\textbf{Answer Key: Identifying Themes and Details}}
\fancyfoot[C]{\footnotesize © Study Smart Tutors}

\begin{document}

\section*{Answer Key: Identifying Themes and Details in Text}

\subsection*{Guided Practice Answers}
\begin{enumerate}
    \item \textbf{What lesson does Maya learn in the story?}
    Maya learns that patience and hard work lead to great results. This is shown when her grandmother tells her, “Good things take time,” and when the garden eventually grows into something beautiful.
    
    \item \textbf{What is the theme of the story?}
    The theme is that patience and effort can lead to rewarding outcomes.
\end{enumerate}

\subsection*{Independent Practice Answers}
\begin{enumerate}
    \item \textbf{Underline:} 
    - Beginning of the story: “I worked so hard, and it still wasn’t enough,” she said, tears streaming down her face.
    - End of the story: “Your improvement is incredible,” the coach said.

    \item \textbf{Box:} Lila’s problem is that she did not make the school soccer team despite working hard.

    \item \textbf{What lesson does Lila learn in this story?}
    Lila learns that perseverance and continued effort can lead to success over time.

    \item \textbf{What is the theme of the story?}
    The theme is perseverance and determination can help you overcome challenges and achieve your goals.
\end{enumerate}

\subsection*{Exit Ticket Sample Answer}
\textbf{How is a theme different from a summary of the story?}

A theme is the general message or lesson about life or people, like “hard work pays off.” A summary is a brief description of the main events and details in the story.

\end{document}
