\documentclass[12pt]{article}
\usepackage[a4paper, top=0.8in, bottom=0.7in, left=0.8in, right=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{tcolorbox}
\usepackage[defaultfam,tabular,lining]{montserrat}

\setlength{\parindent}{0pt}
\pagestyle{fancy}

\fancyhf{}
\fancyhead[L]{\textbf{Answer Key: Main Idea and Supporting Details}}
\fancyfoot[C]{\footnotesize © Study Smart Tutors}

\begin{document}

\section*{Answer Key: Main Idea and Supporting Details}

\subsection*{Guided Practice Answers}

\begin{enumerate}[itemsep=1em]
    \item \textbf{Main Idea:} Books can take you to different places, teach you new ideas, and make you smarter. 
    \item \textbf{Supporting Sentence (Check Your Work):} Reading is a fun activity that can make you smarter, more creative, and happier.
\end{enumerate}

\subsection*{Independent Practice Answer}

\textbf{Main Idea:} Cats are the best pets because they are independent, clean, helpful, and quiet.

\textbf{Supporting Details:}
\begin{itemize}
    \item Cats are independent and don’t need as much attention as other pets like dogs.
    \item Cats groom themselves, so they don’t need frequent bathing.
    \item Cats are natural hunters and can help keep mice away.
    \item Cats are quiet pets, which makes them good for apartments or places with noise restrictions.
\end{itemize}

\subsection*{Exit Ticket Sample Answer}

\textbf{Sample Sentence:} I think cats are the best pets because they are quiet and don’t bark, which is perfect for living in an apartment.

\end{document}
