\documentclass[12pt]{article}
\usepackage[a4paper, top=0.8in, bottom=0.7in, left=0.8in, right=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{tcolorbox}
\usepackage[defaultfam,tabular,lining]{montserrat}

\setlength{\parindent}{0pt}
\pagestyle{fancy}

\fancyhf{}
\fancyhead[L]{\textbf{Answer Key: Relative Pronouns and Relative Adverbs}}
\fancyfoot[C]{\footnotesize © Study Smart Tutors}

\begin{document}

\section*{Answer Key: Relative Pronouns and Relative Adverbs}

\subsection*{Guided Practice Answers}
\begin{enumerate}[itemsep=1em]
    \item The boy \textbf{who} found the missing wallet was rewarded.
    \item The book \textbf{that} I borrowed from the library is about space.
    \item Do you know the reason \textbf{why} she is upset?
    \item This is the house \textbf{where} my grandparents lived for 50 years.
    \item The teacher \textbf{whose} class we love is retiring next year.
\end{enumerate}

\subsection*{Independent Practice Answers}
Underline the relative pronoun or relative adverb in each sentence:
\begin{enumerate}[itemsep=1em]
    \item I visited the museum \underline{\textbf{where}} ancient artifacts are displayed.
    \item The girl \underline{\textbf{who}} won the contest is my cousin.
    \item This is the reason \underline{\textbf{why}} we need to finish our project on time.
    \item My father, \underline{\textbf{whose}} car is in the shop, is taking the bus to work today.
    \item They found the treasure \underline{\textbf{that}} was hidden for centuries.
\end{enumerate}

\subsection*{Exit Ticket Sample Answer}
\textbf{Sentence:} The park \underline{\textbf{where}} we had a picnic was beautiful, and the man \underline{\textbf{who}} organized the event was very kind.

\end{document}
