\documentclass[12pt]{article}
\usepackage[a4paper, top=0.8in, bottom=0.7in, left=0.8in, right=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{tcolorbox}
\usepackage[defaultfam,tabular,lining]{montserrat}

\setlength{\parindent}{0pt}
\pagestyle{fancy}
\setlength{\headheight}{27.11148pt}
\addtolength{\topmargin}{-15.11148pt}
\fancyhf{}
\fancyhead[L]{\textbf{Grading Guide: Opinion Writing}}
\fancyfoot[C]{\footnotesize \textcopyright Study Smart Tutors}
\sloppy

\begin{document}

\section*{Grading Guide for Writing Prompt}

\subsection*{Scoring Categories and Points}

\begin{tcolorbox}[colframe=black!40, colback=gray!5, title={Purpose, Focus, and Organization (0--4 points)}]
\textbf{4 Points:} The response is focused, with a clear opinion, strong introduction, logical structure, and a strong conclusion. Ideas flow smoothly and are well-organized. \\
\textbf{3 Points:} The response is mostly focused and organized, with a clear opinion, but some areas lack development or logical flow. \\
\textbf{2 Points:} The response shows an attempt to focus on the prompt but lacks a clear structure, or some parts are unrelated to the opinion. \\
\textbf{1 Point:} The response lacks focus or organization, and the opinion is unclear. \\
\textbf{0 Points:} The response does not address the prompt or lacks any clear opinion or structure.
\end{tcolorbox}

\begin{tcolorbox}[colframe=black!40, colback=gray!5, title=Evidence and Elaboration (0--4 points)]
\textbf{4 Points:} The response provides strong evidence from multiple sources to support the opinion. Explanations of how evidence supports the opinion are clear and well-elaborated. Linking words and phrases are used effectively. \\
\textbf{3 Points:} The response provides sufficient evidence from the sources, but explanations are somewhat underdeveloped or repetitive. \\
\textbf{2 Points:} The response provides limited evidence from the sources and may include irrelevant or poorly explained details. \\
\textbf{1 Point:} The response includes minimal evidence or no clear connection between the evidence and the opinion. \\
\textbf{0 Points:} The response does not provide evidence or use the sources.
\end{tcolorbox}

\begin{tcolorbox}[colframe=black!40, colback=gray!5, title=Conventions of Standard English (0--2 points)]
\textbf{2 Points:} The response demonstrates a strong command of grammar, punctuation, capitalization, and spelling, with few to no errors. \\
\textbf{1 Point:} The response shows a basic command of conventions, but there are noticeable errors that do not interfere with meaning. \\
\textbf{0 Points:} The response has significant errors that make it difficult to understand.
\end{tcolorbox}

\subsection*{Rubric at a Glance}
\begin{tcolorbox}[colframe=black!40, colback=white, title=Score Distribution]
\begin{tabular}{|p{4cm}|p{2cm}|p{2cm}|p{2cm}|p{2cm}|}
\hline
\textbf{Category} & \textbf{4 Points} & \textbf{3 Points} & \textbf{2 Points} & \textbf{1 Point} \\ \hline
\textbf{Purpose, Focus, Organization} & Clear opinion, strong structure & Mostly clear opinion, minor flaws & Attempted focus, lacks structure & Unclear or disorganized \\ \hline
\textbf{Evidence and Elaboration} & Strong evidence, clear explanations & Sufficient evidence, weak explanations & Limited evidence, underdeveloped & Minimal evidence, unclear connections \\ \hline
\textbf{Conventions} & Few to no errors & Some errors, minor impact & Noticeable errors & Significant errors \\ \hline
\end{tabular}
\end{tcolorbox}

\subsection*{Total Points: 10}
\begin{tcolorbox}[colframe=black!40, colback=white, title=Score Levels]
\textbf{8--10 Points:} Exemplary response that clearly addresses the prompt with strong support and minimal errors. \\
\textbf{5--7 Points:} Proficient response that addresses the prompt with sufficient support but may lack full development or contain minor errors. \\
\textbf{3--4 Points:} Basic response with limited evidence or structure. Significant errors or underdeveloped ideas may be present. \\
\textbf{0--2 Points:} Inadequate response that does not address the prompt effectively or lacks structure and evidence.
\end{tcolorbox}

\subsection*{Additional Grading Tips}
\begin{tcolorbox}[colframe=black!40, colback=gray!5]
\begin{itemize}
    \item \textbf{Check for Source Integration:} Ensure students reference both sources and provide specific evidence.
    \item \textbf{Evaluate Logical Flow:} Look for linking phrases like \textit{“in addition,” “for example,” “therefore”}.
    \item \textbf{Balance Between Opinions and Evidence:} Ensure opinions are supported by evidence and not simply restated.
    \item \textbf{Encourage Strong Conclusions:} Check for restated opinions and final thoughts in conclusions.
\end{itemize}
\end{tcolorbox}

\end{document}
