\documentclass[12pt]{article}
\usepackage[a4paper, top=0.8in, bottom=0.7in, left=0.8in, right=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float} % Helps with precise image placement
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{tcolorbox}
\usepackage[defaultfam,tabular,lining]{montserrat} % Font settings for Montserrat

\setlength{\parindent}{0pt}
\pagestyle{fancy}

\fancyhf{}
\fancyhead[L]{\textbf{Answer Key: Identifying and Retelling Main Ideas}}
\fancyfoot[C]{\footnotesize © Study Smart Tutors}

\begin{document}

\section*{Answer Key: Identifying and Retelling Main Ideas of Stories}

\subsection*{Text: The Adventures of Benny and the Blue Balloon}

\textbf{Main Idea:} If you care about something, you should take good care of it.

\textbf{Key Details:}
\begin{itemize}
    \item Benny tied the balloon to his wrist so it wouldn’t float away.
    \item Benny chased the balloon across the park when it blew away.
    \item Benny climbed a tree to rescue the balloon and tied it securely to his wrist with a double knot.
\end{itemize}

\textbf{Paraphrased Retelling:} Benny loved his blue balloon and tied it to his wrist so it wouldn’t float away. One day, the balloon got loose and flew into a tree. Benny worked hard to get it back by climbing the tree and tying it securely with a double knot. From then on, he always took great care of it.

\vspace{1em}

\subsection*{Text: Sammy and the Missing Sandwich}

\textbf{Main Idea:} Sharing and kindness are important when solving problems with friends.

\textbf{Key Details:}
\begin{itemize}
    \item Sammy’s sandwich went missing while he played with his friends.
    \item He followed crumbs and found Benny the bunny eating the sandwich.
    \item Sammy forgave Benny and suggested sharing in the future.
    \item Sammy packed two sandwiches the next day so they could share lunch.
\end{itemize}

\textbf{Paraphrased Retelling:} Sammy discovered his sandwich was missing and followed crumbs to find Benny the bunny eating it. Benny apologized, and Sammy forgave him, suggesting they share in the future. The next day, Sammy brought two sandwiches so they could eat together.

\vspace{1em}

\subsection*{Text: The Mystery of the Missing Homework}

\textbf{Main Idea:} Staying organized can help solve problems.

\textbf{Key Details:}
\begin{itemize}
    \item Ella realized her homework was missing from her backpack.
    \item She retraced her steps and remembered putting it in her folder.
    \item After carefully checking her backpack, she found her homework at the bottom.
    \item Ella made a plan to stay organized and became the go-to problem solver in her class.
\end{itemize}

\textbf{Paraphrased Retelling:} Ella couldn’t find her homework and retraced her steps to figure out what happened. She checked her backpack more carefully and found it at the bottom. After solving the mystery, she made a plan to stay organized and became known for helping others solve problems.

\vspace{1em}

\subsection*{Independent Practice: Time Limits for Video Games}

\textbf{Main Idea:} Kids should limit how much time they spend playing video games to stay healthy and happy.

\textbf{Key Details:}
\begin{itemize}
    \item Sitting too long while playing video games can affect your body and make you feel tired.
    \item Too much screen time can hurt your eyes and disrupt your sleep.
    \item Kids need time for other activities like playing outside, reading, or spending time with family.
\end{itemize}

\textbf{Correct Choices for Details:}
\begin{itemize}
    \item \textbf{Correct:} It’s important to get exercise.
    \item \textbf{Correct:} Too much screen time affects sleep.
    \item \textbf{Correct:} Kids need time for other activities.
    \item \textbf{Incorrect:} Video games can cause toothaches.
    \item \textbf{Incorrect:} Playing video games can make you shorter.
    \item \textbf{Incorrect:} Video games are illegal in some places.
\end{itemize}

\textbf{Exit Ticket:} Answers will vary but should include valid reasons and supporting details for the main idea.

\end{document}
