\documentclass[12pt]{article}
\usepackage[a4paper, top=0.8in, bottom=0.7in, left=0.8in, right=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{tcolorbox}
\usepackage[defaultfam,tabular,lining]{montserrat}

\setlength{\parindent}{0pt}
\pagestyle{fancy}

\fancyhf{}
\fancyhead[L]{\textbf{Answer Key: Simple, Complex, and Compound Sentences}}
\fancyfoot[C]{\footnotesize © Study Smart Tutors}

\begin{document}

\section*{Answer Key: Simple, Complex, and Compound Sentences}

\subsection*{Guided Practice: Identifying Subject and Predicate}
\begin{enumerate}
    \item \textbf{Subject:} I \textbf{Predicate:} cannot drink warm soda.
    \item \textbf{Subject:} My guinea pig \textbf{Predicate:} is orange and white.
    \item \textbf{Subject:} A day without sunshine \textbf{Predicate:} is depressing.
    \item \textbf{Subject:} My alarm clock \textbf{Predicate:} wakes me up for school.
    \item \textbf{Subject:} They \textbf{Predicate:} are coming with me to the swimming pool.
\end{enumerate}

\subsection*{Guided Practice: Complex Sentences}
\begin{enumerate}
    \item I love going outside \textbf{\underline{when}} \underline{the weather is warm}.
    \item My cat sleeps a lot \textbf{\underline{after}} \underline{being out all night}.
    \item I would have given you my lunch \textbf{\underline{if}} \underline{I hadn't left it at home}.
\end{enumerate}

\subsection*{Guided Practice: Compound Sentences}
\begin{enumerate}
    \item We got wet in the rain, \textbf{so} we changed our clothes.
    \item I thought I could eat one hundred chicken wings, \textbf{but} I was wrong.
    \item Elephants are the largest land animals, \textbf{and} blue whales are the largest animals on Earth.
    \item I often travel to other countries, \textbf{for} I want to learn many languages.
\end{enumerate}

\subsection*{Independent Practice}
\begin{enumerate}
    \item The red apple is the most delicious. (\textbf{Simple Sentence})  
    Independent Clause: \underline{The red apple is the most delicious}.
    
    \item I wanted to eat the apple, \textbf{so} I picked it from my neighbor's tree. (\textbf{Compound Sentence})  
    Independent Clauses: \underline{I wanted to eat the apple}, \underline{I picked it from my neighbor's tree}.
    
    \item My neighbor saw me pick his fruit; he was not happy with me. (\textbf{Compound Sentence})  
    Independent Clauses: \underline{My neighbor saw me pick his fruit}, \underline{he was not happy with me}.
    
    \item I apologized to my neighbor \textbf{after} he yelled. (\textbf{Complex Sentence})  
    Independent Clause: \underline{I apologized to my neighbor}.  
    Dependent Clause: \underline{after he yelled}.
\end{enumerate}

\subsection*{Exit Ticket}
\textbf{Sample Answer:}  
When the bell rings, I will go to the cafeteria.  
- **Complex Sentence:**  
  - **Independent Clause:** \underline{I will go to the cafeteria}.  
  - **Dependent Clause:** \underline{When the bell rings}.

\end{document}
