\documentclass[12pt]{article}
\usepackage[a4paper, top=0.8in, bottom=0.7in, left=0.8in, right=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{latexsym}
\usepackage{graphicx}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{tcolorbox}
\usepackage[defaultfam,tabular,lining]{montserrat}

\setlength{\parindent}{0pt}
\pagestyle{fancy}

\fancyhf{}
\fancyhead[L]{\textbf{Answer Key: Understanding Characters and Their Actions}}
\fancyfoot[C]{\footnotesize \textcopyright Study Smart Tutors}

\begin{document}

\section*{Answer Key: Understanding Characters and Their Actions}

\subsection*{Text: The Lost Puppy Adventure}

\textbf{Main Idea:} The kids' kindness and determination helped them find the puppy's owner.

\textbf{Character Traits, Motivations, and Actions:}
\begin{itemize}
    \item \textbf{Mia:} Brave and kind. She suggested finding the owner and took the lead.
    \item \textbf{Jack:} Observant and helpful. He spotted the flyer and read it aloud.
    \item \textbf{Ella:} Gentle and caring. She comforted the puppy and helped search for the owner.
\end{itemize}

\textbf{Sequence of Events:}
\begin{itemize}
    \item The kids heard the puppy whimpering and decided to help.
    \item They asked people in the park if anyone had lost the puppy.
    \item Jack found a missing puppy flyer, and they called the owner.
    \item The owner arrived, reunited with the puppy, and rewarded the kids.
\end{itemize}

\vspace{1em}

\subsection*{Text: Leo and the Big Game}

\textbf{Main Idea:} Believing in yourself and staying focused can lead to success.

\textbf{Character Traits, Motivations, and Actions:}
\begin{itemize}
    \item \textbf{Leo:} Nervous but determined. His coach’s advice motivated him to stay focused and try his best.
\end{itemize}

\textbf{Key Details:}
\begin{itemize}
    \item Leo felt nervous before the game but remembered his coach's words: “Stay focused and don’t give up.”
    \item Despite the opposing team scoring first, Leo concentrated and blocked the final shot.
    \item His determination helped his team win the championship.
\end{itemize}

\vspace{1em}

\subsection*{Text: The Great Garden Rescue}

\textbf{Main Idea:} Working together makes difficult tasks easier.

\textbf{Character Traits, Motivations, and Actions:}
\begin{itemize}
    \item \textbf{Lila:} Encouraging and hardworking. She motivated Max to keep going.
    \item \textbf{Max:} Initially frustrated but determined. He continued weeding with Lila’s encouragement.
\end{itemize}

\textbf{Sequence of Events:}
\begin{itemize}
    \item Lila and Max discovered weeds choking their garden.
    \item Lila suggested pulling out the weeds and encouraged Max when he wanted to stop.
    \item They worked together and cleared the weeds, making the garden beautiful again.
\end{itemize}

\vspace{1em}

\subsection*{Independent Practice}

\textbf{Text: The Great Garden Rescue}

\textbf{Max’s Traits:} Initially frustrated, but willing to work hard with encouragement.

\textbf{Motivation:} He wanted the flowers to grow and the garden to look beautiful again.

\textbf{Actions:} Max pulled weeds with Lila until the garden was cleared.

\vspace{1em}

\subsection*{Exit Ticket}

\textbf{Example:}
\begin{itemize}
    \item \textbf{Picture Description:} Draw the moment when Leo blocks the shot that helps his team win the game. Write: “Leo’s determination helped him block the shot and win the championship.”
\end{itemize}

\end{document}
