\documentclass[12pt]{article}
\usepackage[a4paper, top=0.8in, bottom=0.7in, left=0.8in, right=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{tcolorbox}
\usepackage[defaultfam,tabular,lining]{montserrat}

\setlength{\parindent}{0pt}
\pagestyle{fancy}

\fancyhf{}
\fancyhead[L]{\textbf{Answer Key: Identifying Main Idea and Supporting Details}}
\fancyfoot[C]{\footnotesize \copyright Study Smart Tutors}

\begin{document}

\section*{Answer Key: Identifying Main Idea and Supporting Details}

\subsection*{Main Idea and Supporting Details: \textit{Why Brushing Your Teeth is Important}}
\textbf{Main Idea:} Brushing your teeth is essential for maintaining oral and overall health.

\textbf{Supporting Details:}
\begin{itemize}
    \item Brushing removes plaque, which can cause cavities and make it hard to eat your favorite foods.
    \item Brushing keeps your gums healthy, preventing gum disease that can make teeth loose.
    \item It helps keep your breath fresh and makes you feel confident when talking to people.
\end{itemize}

\subsection*{Main Idea and Supporting Details: \textit{Should You Learn Another Language?}}
\textbf{Main Idea:} Learning another language is a smart and beneficial choice.

\textbf{Supporting Details:}
\begin{itemize}
    \item It helps you communicate with more people, especially if you travel to another country.
    \item Learning another language improves your brain by enhancing problem-solving and memory skills.
    \item It can help you succeed in school and get a good job, making you stand out.
    \item It teaches you about other cultures, including their food, music, and traditions.
\end{itemize}

\subsection*{Independent Practice: \textit{Time Limits for Video Games}}
\textbf{Main Idea:} Kids should limit their video game time to stay healthy and happy.

\textbf{Details Supporting the Main Idea:}
\begin{itemize}
    \item Sitting for long periods can affect your body, making you feel tired and less energetic.
    \item Too much screen time can harm your eyes and disrupt your sleep schedule.
    \item Limiting video games allows time for other activities like reading, homework, or playing outside.
\end{itemize}

\textbf{Incorrect Details:}
\begin{itemize}
    \item Video games can cause toothaches.
    \item Playing video games can make you shorter.
    \item Video games are illegal in some places.
\end{itemize}

\subsection*{Exit Ticket: Sample Response}
\textbf{Question:} Do you think kids should be allowed to spend as much time playing video games as they want? Support your main idea with two details.

\textbf{Sample Answer:} No, kids should not be allowed to spend as much time playing video games as they want. Too much screen time can harm their eyes and disrupt their sleep. Additionally, kids need time for other important activities like exercise and homework.

\end{document}
