\documentclass[12pt]{article}
\usepackage[a4paper, top=0.8in, bottom=0.7in, left=0.8in, right=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{tcolorbox}
\usepackage[defaultfam,tabular,lining]{montserrat}

\setlength{\parindent}{0pt}
\pagestyle{fancy}

\fancyhf{}
\fancyhead[L]{\textbf{Grading Guide: Opinion Writing}}
\fancyfoot[C]{\footnotesize \textcopyright Study Smart Tutors}

\begin{document}

\section*{Grading Guide for Opinion Writing Assignment}

\subsection*{Criteria and Scoring Rubric}

Each student’s written response will be evaluated using the following criteria. Assign a score between 0-4 for each category.

\begin{tcolorbox}[colframe=black!60, colback=white, title=Purpose, Focus, and Organization]
\textbf{Criteria:}
\begin{itemize}
    \item Clear opinion stated in the introduction.
    \item Writing is well-organized with a logical flow of ideas.
    \item Includes an introduction, body (supporting details), and conclusion.
\end{itemize}
\textbf{Scoring:}
\begin{itemize}
    \item 4 - Opinion is clearly stated, with strong organization and transitions between ideas.
    \item 3 - Opinion is stated, with minor lapses in organization or flow.
    \item 2 - Opinion is unclear or not restated in the conclusion; structure needs improvement.
    \item 1 - Opinion is missing or disorganized; lacks an introduction or conclusion.
    \item 0 - No opinion or structure is present.
\end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[colframe=black!60, colback=white, title=Evidence and Elaboration]
\textbf{Criteria:}
\begin{itemize}
    \item Includes at least two reasons supported by evidence from the sources.
    \item Evidence is explained clearly and connects to the opinion.
    \item Uses linking words (e.g., "because," "for example," "since") to connect ideas.
\end{itemize}
\textbf{Scoring:}
\begin{itemize}
    \item 4 - Two or more reasons are strongly supported with relevant evidence and clear explanations.
    \item 3 - Two reasons are included but may lack sufficient evidence or explanation.
    \item 2 - Only one reason is supported, or explanations are unclear or incomplete.
    \item 1 - Minimal evidence is included; reasons are unsupported or unclear.
    \item 0 - No evidence or elaboration is present.
\end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[colframe=black!60, colback=white, title=Language and Conventions]
\textbf{Criteria:}
\begin{itemize}
    \item Sentences are complete and varied.
    \item Correct spelling, punctuation, and grammar are used.
    \item Uses appropriate vocabulary for the grade level.
\end{itemize}
\textbf{Scoring:}
\begin{itemize}
    \item 4 - Minimal to no errors in conventions; sentences are clear and well-constructed.
    \item 3 - A few errors in conventions that do not interfere with meaning.
    \item 2 - Errors in conventions occasionally interfere with understanding.
    \item 1 - Frequent errors in conventions that interfere with meaning.
    \item 0 - Writing is incomprehensible due to numerous errors.
\end{itemize}
\end{tcolorbox}

\subsection*{Scoring Total}
Calculate the total score by adding the points from each category:
\begin{align*}
\text{Total Score: } & \text{(Purpose, Focus, and Organization)} + \text{(Evidence and Elaboration)} + \text{(Language and Conventions)} \\
\text{Maximum Score: } & 12 \text{ points.}
\end{align*}

\subsection*{Performance Levels}
\begin{itemize}
    \item \textbf{10-12:} Exemplary - Writing is clear, focused, and well-supported with minimal errors.
    \item \textbf{7-9:} Proficient - Writing meets most criteria with minor lapses in focus, evidence, or conventions.
    \item \textbf{4-6:} Developing - Writing partially meets criteria; lacks clarity or sufficient support.
    \item \textbf{0-3:} Beginning - Writing does not meet criteria; little to no evidence of opinion or structure.
\end{itemize}

\end{document}
