\documentclass[12pt]{article}
\usepackage[a4paper, top=0.8in, bottom=0.7in, left=0.8in, right=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{tcolorbox}
\usepackage[defaultfam,tabular,lining]{montserrat}

\setlength{\parindent}{0pt}
\pagestyle{fancy}

\fancyhf{}
\fancyhead[L]{\textbf{Grading Guide: Opinion Writing}}
\fancyfoot[C]{\footnotesize \textcopyright Study Smart Tutors}

\begin{document}

\section*{Grading Guide: Opinion Writing Assignment (Pass/Fail)}

\subsection*{Criteria for Passing}

To pass, a student’s written response must meet the following minimum requirements in all three categories, aligned to Standard 3.W.1:

\begin{tcolorbox}[colframe=black!60, colback=white, title=Purpose, Focus, and Organization]
\textbf{Pass Requirements:}
\begin{itemize}
    \item Clearly states an opinion related to the topic or prompt.
    \item Includes a clear structure with:
    \begin{itemize}
        \item \textbf{Introduction:} Provides context for the opinion and introduces the topic.
        \item \textbf{Body:} Contains organized paragraphs with reasons and evidence.
        \item \textbf{Conclusion:} Restates the opinion and summarizes key points.
    \end{itemize}
    \item The writing stays focused on the assigned topic or prompt.
\end{itemize}

\textbf{Fail:}
\begin{itemize}
    \item No opinion is stated, or the response lacks structure or focus.
    \item Missing one or more required sections (introduction, body, conclusion).
\end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[colframe=black!60, colback=white, title=Evidence and Elaboration]
\textbf{Pass Requirements:}
\begin{itemize}
    \item Provides at least two reasons to support the opinion.
    \item Uses evidence from at least one source to explain or justify the reasons.
    \item Connects reasons and evidence using linking words (e.g., “because,” “since,” “for example”).
    \item Explains how the evidence supports the opinion.
\end{itemize}

\textbf{Fail:}
\begin{itemize}
    \item Fewer than two reasons are provided, or the reasons lack evidence or explanation.
    \item No evidence from the sources is included, or evidence is irrelevant.
    \item Linking words are not used, making the writing unclear.
\end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[colframe=black!60, colback=white, title=Language and Conventions]
\textbf{Pass Requirements:}
\begin{itemize}
    \item Sentences are complete, clear, and appropriate for the grade level.
    \item Few errors in spelling, punctuation, and grammar that do not interfere with understanding.
    \item Vocabulary is appropriate for the audience and task.
\end{itemize}

\textbf{Fail:}
\begin{itemize}
    \item Frequent errors in spelling, punctuation, or grammar interfere with understanding.
    \item Sentences are incomplete or unclear.
\end{itemize}
\end{tcolorbox}

\subsection*{Final Determination}

\begin{tcolorbox}[colframe=black!60, colback=white, title=How to Determine Pass/Fail]
\textbf{Pass:}
\begin{itemize}
    \item Meets all requirements in each of the three categories.
\end{itemize}

\textbf{Fail:}
\begin{itemize}
    \item Does not meet the minimum requirements in one or more categories.
\end{itemize}
\end{tcolorbox}

\subsection*{Teacher Notes}
\begin{itemize}
    \item Encourage students to review their writing to ensure it meets the passing requirements.
    \item If a response is borderline, provide specific feedback to help the student revise and meet expectations.
    \item Highlight areas where the student excelled in addition to areas for improvement.
\end{itemize}

\end{document}
