\documentclass[12pt]{article}
\usepackage[a4paper, top=0.8in, bottom=0.7in, left=0.8in, right=0.8in]{geometry}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{float}
\usepackage{fancyhdr}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage{tcolorbox}
\usepackage[defaultfam,tabular,lining]{montserrat}

\setlength{\parindent}{0pt}
\pagestyle{fancy}

\fancyhf{}
\fancyhead[L]{\textbf{Grading Guide: Opinion Writing (Pass/Fail)}}
\fancyfoot[C]{\footnotesize \textcopyright Study Smart Tutors}

\begin{document}

\section*{Grading Guide: Opinion Writing Assignment (Pass/Fail)}

\subsection*{Criteria for Passing}

To pass, a student’s written response must meet the following minimum requirements in all three categories:

\begin{tcolorbox}[colframe=black!60, colback=white, title=Purpose, Focus, and Organization]
\textbf{Pass Requirements:}
\begin{itemize}
    \item Clearly states an opinion in the introduction.
    \item Includes a clear structure with an introduction, body (reasons and evidence), and conclusion.
    \item The writing stays focused on the assigned topic or prompt.
\end{itemize}

\textbf{Fail:}
\begin{itemize}
    \item No opinion is stated, or the response lacks structure or focus.
\end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[colframe=black!60, colback=white, title=Evidence and Elaboration]
\textbf{Pass Requirements:}
\begin{itemize}
    \item Provides at least two reasons supporting the opinion.
    \item Uses evidence from at least one source to support the reasons.
    \item Explains how the evidence connects to the opinion.
    \item Uses linking words (e.g., "because," "since," "for example") to connect ideas.
\end{itemize}

\textbf{Fail:}
\begin{itemize}
    \item Fewer than two reasons are provided, or the reasons lack evidence or explanation.
    \item No evidence from the sources is included, or evidence is irrelevant.
\end{itemize}
\end{tcolorbox}

\begin{tcolorbox}[colframe=black!60, colback=white, title=Language and Conventions]
\textbf{Pass Requirements:}
\begin{itemize}
    \item Sentences are complete and readable.
    \item Few errors in spelling, punctuation, and grammar that do not interfere with understanding.
    \item Uses vocabulary appropriate for the grade level.
\end{itemize}

\textbf{Fail:}
\begin{itemize}
    \item Frequent errors in spelling, punctuation, or grammar interfere with understanding.
    \item Writing is incomplete or difficult to read.
\end{itemize}
\end{tcolorbox}

\subsection*{Final Determination}

\begin{tcolorbox}[colframe=black!60, colback=white, title=How to Determine Pass/Fail]
\textbf{Pass:}
\begin{itemize}
    \item Meets all requirements in each of the three categories.
\end{itemize}

\textbf{Fail:}
\begin{itemize}
    \item Does not meet the minimum requirements in one or more categories.
\end{itemize}
\end{tcolorbox}

\subsection*{Teacher Notes}
\begin{itemize}
    \item Encourage students to review their writing to ensure it meets the passing requirements.
    \item If a response is borderline, provide specific feedback to help the student revise and meet expectations.
\end{itemize}

\end{document}
